### 2025-07-08 evaluating-prediction-accuracy.qmd
20250703 - fix heading hierarchy (https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook/issues/7)
To address issue https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook/issues/7
20250708 - track chunk execution times
20250708 - packages and citations

@@

### Weekly Projections {#sec-predictionAccuracyPrepareDataWeekly}

@@

```{r}
#| label: fig-calibrationPlotSeasonalOverall
#| fig-cap: "Calibration Plot for Seasonal Projections. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalQBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Quarterbacks. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Quarterbacks. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalRBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Running Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Running Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalWRs
#| fig-cap: "Calibration Plot for Seasonal Projections of Wide Receivers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Wide Receivers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalTEs
#| fig-cap: "Calibration Plot for Seasonal Projections of Tight Ends. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Tight Ends. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalKs
#| fig-cap: "Calibration Plot for Seasonal Projections of Kickers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Kickers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalDLs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Linemen. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Linemen. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalLBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Linebackers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Linebackers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalDBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyOverall
#| fig-cap: "Calibration Plot for Weekly Projections. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyQBs
#| fig-cap: "Calibration Plot for Weekly Projections of Quarterbacks. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Quarterbacks. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyRBs
#| fig-cap: "Calibration Plot for Weekly Projections of Running Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Running Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyWRs
#| fig-cap: "Calibration Plot for Weekly Projections of Wide Receivers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Wide Receivers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyTEs
#| fig-cap: "Calibration Plot for Weekly Projections of Tight Ends. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Tight Ends. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyKs
#| fig-cap: "Calibration Plot for Weekly Projections of Kickers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Kickers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyDLs
#| fig-cap: "Calibration Plot for Weekly Projections of Defensive Linemen. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Defensive Linemen. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyLBs
#| fig-cap: "Calibration Plot for Weekly Projections of Linebackers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Linebackers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyDBs
#| fig-cap: "Calibration Plot for Weekly Projections of Defensive Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Defensive Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

>>>>

{{< include _chunk-timing.qmd >}}

@@

#### Weekly Projections {#sec-predictionAccuracyPrepareDataWeekly}

@@

We calculate the 95% prediction interval based on a LOESS model, which allows nonlinear associations, using the `loess.sd()` function of the `msir` package [@R-msir; @Scrucca2011_packages].

```{r}
#| label: fig-calibrationPlotSeasonalOverall
#| fig-cap: "Calibration Plot for Seasonal Projections. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalQBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Quarterbacks. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Quarterbacks. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalRBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Running Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Running Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalWRs
#| fig-cap: "Calibration Plot for Seasonal Projections of Wide Receivers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Wide Receivers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalTEs
#| fig-cap: "Calibration Plot for Seasonal Projections of Tight Ends. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Tight Ends. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalKs
#| fig-cap: "Calibration Plot for Seasonal Projections of Kickers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Kickers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalDLs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Linemen. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Linemen. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalLBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Linebackers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Linebackers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalDBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyOverall
#| fig-cap: "Calibration Plot for Weekly Projections. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-alt: "Calibration Plot for Weekly Projections. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyQBs
#| fig-cap: "Calibration Plot for Weekly Projections of Quarterbacks. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-alt: "Calibration Plot for Weekly Projections of Quarterbacks. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyRBs
#| fig-cap: "Calibration Plot for Weekly Projections of Running Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-alt: "Calibration Plot for Weekly Projections of Running Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyWRs
#| fig-cap: "Calibration Plot for Weekly Projections of Wide Receivers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-alt: "Calibration Plot for Weekly Projections of Wide Receivers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyTEs
#| fig-cap: "Calibration Plot for Weekly Projections of Tight Ends. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-alt: "Calibration Plot for Weekly Projections of Tight Ends. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyKs
#| fig-cap: "Calibration Plot for Weekly Projections of Kickers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-alt: "Calibration Plot for Weekly Projections of Kickers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyDLs
#| fig-cap: "Calibration Plot for Weekly Projections of Defensive Linemen. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-alt: "Calibration Plot for Weekly Projections of Defensive Linemen. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyLBs
#| fig-cap: "Calibration Plot for Weekly Projections of Linebackers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-alt: "Calibration Plot for Weekly Projections of Linebackers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyDBs
#| fig-cap: "Calibration Plot for Weekly Projections of Defensive Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-alt: "Calibration Plot for Weekly Projections of Defensive Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points based on a locally estimated scatterplot smoothing (LOESS) model."
#| fig-width: 8
#| fig-height: 6

### 2025-07-08 getting-started.qmd
20250708 - track chunk execution times
20250708 - packages and citations

   install.packages(
     c("petersenlab","remotes","knitr","rmarkdown","dplyr",
       "ggplot2","tidyverse","psych","xfun","downlit","xml2",
       "nflreadr","nflplotR","nflfastR","nflseedR","nfl4th",
       "gsisdecoder","progressr","DescTools","pwr","pwrss",
       "WebPower","XICOR","dagitty","ggdag","lubridate",
       "ggtext","gghighlight","ggExtra","grid","patchwork",
       "pROC","lme4","lmerTest","MuMIn","emmeans","pbkrtest",
       "sjstats","AICcmodavg","rstan","brms","bbmle",
       "fitdistrplus","mclust","magrittr","viridis","viridisLite",
       "msir","plotly","webshot2","quantmod","fPortfolio",
       "xts","zoo","forecast","stringi","parallel","parallelly",
       "doParallel","missRanger","powerjoin","caret","gpboost",
       "ggridges","corrplot","rms","car","caret","performance",
       "correlation","interactions","lavaan","mice","miceadds",
       "robustbase","see"))
   ```
1. Some necessary packages, including the [`ffanalytics` package](https://github.com/FantasyFootballAnalytics/ffanalytics) [@R-ffanalytics], are hosted in GitHub (and are not hosted on the Comprehensive R Archive Network [CRAN]) and thus need to be installed using the following code (after installing the `remotes` package [@R-remotes] above)[^petersenlabPackageGitHub]:
   ```{r}
   #| eval: false

>>>>

   install.packages(c(
     "petersenlab","remotes","knitr","rmarkdown","dplyr","ggplot2","tidyverse",
     "broom","broom.mixed","psych","downlit","xml2","nflreadr","nflplotR",
     "nflfastR","nflseedR","nfl4th","gsisdecoder","progressr","DescTools",
     "pwr","pwrss","WebPower","XICOR","dagitty","ggdag","lubridate","ggtext",
     "gghighlight","ggExtra","grid","patchwork","pROC", "lme4","lmerTest",
     "MuMIn","emmeans","pbkrtest","sjstats","AICcmodavg","rstan","brms",
     "tidybayes","bbmle","fitdistrplus","sn","mclust","magrittr","viridis",
     "viridisLite","msir","plotly","webshot2","quantmod","fPortfolio","NMOF",
     "nFactors","xts","zoo","forecast","stringi","parallelly","doParallel",
     "missRanger","ggridges","powerjoin","caret","tidymodels","LongituRF",
     "gpboost","corrplot","correlation","mgcv","rms","car","performance",
     "lavaan","lavaangui","mice","miceadds","interactions","robustbase",
     "ordinal","MASS","data.table","future","future.apply","see","SimDesign",
     "effectsize"))
   ```
1. Some necessary packages, including the [`ffanalytics` package](https://github.com/FantasyFootballAnalytics/ffanalytics) [@R-ffanalytics], are hosted in GitHub (and are not hosted on the Comprehensive R Archive Network [CRAN]) and thus need to be installed using the following code (after installing the `remotes` package [@R-remotes] above)[^petersenlabPackageGitHub]:
   ```{r}
   #| eval: false

### 2025-07-08 index.qmd
20250708 - packages and citations

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "broom", "broom.mixed", 
  "downlit", "xml2", "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", 
  "patchwork", "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", 
  "sjstats", "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", 
  "fitdistrplus", "sn", "mclust", "magrittr", "viridis", "plotly", "quantmod", 
  "fPortfolio", "NMOF", "nFactors", "xts", "zoo", "forecast", "stringi", #"webshot2"
  "parallel", "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin", 
  "caret", "tidymodels", "LongituRF", "gpboost", "cmdstanr", "learnr", 
  "remotes", "corrplot", "correlation", "mgcv", "rms", "car", "performance", 
  "lavaan", "lavaangui", "mice", "miceadds", "interactions", "shiny", 
  "PearsonDS", "robustbase", "ordinal", "MASS", "data.table", "future", 
  "future.apply", "QuantPsyc", "SimDesign", "effectsize"
)

>>>>

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "broom", "broom.mixed", 
  "psych", "downlit", "xml2", "nflreadr", "nflplotR", "nflfastR", "nflseedR", 
  "nfl4th", "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", 
  "XICOR", "dagitty", "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", 
  "grid", "patchwork", "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", 
  "pbkrtest", "sjstats", "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", 
  "fitdistrplus", "sn", "mclust", "magrittr", "viridis", "viridisLite", "msir", 
  "plotly", "webshot2", "quantmod", "fPortfolio", "NMOF", "nFactors", "xts", 
  "zoo", "forecast", "stringi", "parallelly", "doParallel", "missRanger", 
  "ggridges", "powerjoin", "caret", "tidymodels", "LongituRF", "gpboost", 
  "cmdstanr", "corrplot", "correlation", "mgcv", "rms", "car", "performance", 
  "lavaan", "lavaangui", "mice", "miceadds", "interactions", "robustbase", 
  "ordinal", "MASS", "data.table", "future", "future.apply", "see", "SimDesign", 
  "effectsize", 
  "learnr", "remotes", "shiny", "PearsonDS" # packages that are cited but not used for computation (and thus do not need to be installed by me or readers)
)

### 2025-07-08 machine-learning.qmd
20250708 - track chunk execution times
20250708 - packages and citations

```{r}
library("petersenlab")
library("parallel")
library("future")
library("missRanger")
library("powerjoin")
library("tidymodels")
library("LongituRF")
library("gpboost")
library("effectsize")
library("tidyverse")
library("knitr")
```

@@

num_cores <- parallel::detectCores()
num_true_cores <- parallel::detectCores(logical = FALSE)
```

@@

num_cores <- parallel::detectCores() - 1
num_true_cores <- parallel::detectCores(logical = FALSE) - 1
```

>>>>

```{r}
library("petersenlab")
library("future")
library("missRanger")
library("powerjoin")
library("tidymodels")
library("LongituRF")
library("gpboost")
library("effectsize")
library("tidyverse")
library("knitr")
```

@@

num_cores <- parallelly::availableCores()
num_true_cores <- parallelly::availableCores(logical = FALSE)
```

@@

num_cores <- parallelly::availableCores() - 1
num_true_cores <- parallelly::availableCores(logical = FALSE) - 1
```
